Extrinsic Type Inference (DRAFT 2025-06-09)

### 2025-07-11 extrinsic_type_inference_paper/paper.tex
add notes on recursive types

>>>>

\TODO{
I think the main novelty of my type inference design beyond previous systems is that it can infer recursive types extrinsically and then reason inductively with those types. Do you think that the title should reflect that?
}
\TODO{
e.g. “Extrinsic Reconstruction of Recursive Types”
}
\TODO{
e.g. “Inductive Subtyping over Reconstructed Recursive Types”
}

\TODO{don't need to call out extrinsic, because recursive types are the final hurdle in type inference}

\TODO{if recursive types can be reconstructed than so can everything else}
